Efficient toolkit implementing best practices for principal component analysis of population genetic data

### 2019-11-27 paper-bedpca.tex
add tables and fig need text

\newpage

@@

\newpage
\section*{Supplementary Materials}

@@

\subsection*{Supplementary figures}

@@

\newpage

@@

\newpage

@@

>>>>

@@

\clearpage
\section*{Supplementary Materials}

@@

\subsection*{Sample outlier detection}

@@

\clearpage
\subsection*{Projection onto reference PCA space}

@@

\subsection*{PCA of the UK Biobank}

@@

\begin{figure}[!htpb]
\centerline{\includegraphics[width=0.8\textwidth]{het-col-PC16.png}}
\caption{PC-corrected heterozygosity and number of missing values for individuals of the UK Biobank, colored by their value for PC16.
\label{fig:UKBB-het}}
\end{figure}

% latex table generated in R 3.6.0 by xtable 1.8-4 package
% Wed Nov 27 15:52:34 2019
\begin{table}[ht]
\caption{Correlation between first 20 PC scores of the UK Biobank, both computed using the genotyping chip and mean imputation, but wtih either no quality control on individuals based on high heterozygosity (top), or after removing some individuals based on high heterozygosity (left). PC16 computed without quality control on high heterozygosity completely disappears when performing this quality control.
\label{tab:pca-het}}
\centering
\begin{tabular}{|r|rrrrrrrrrrrrrrrrrrrr|}
  \hline
 & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 & 11 & 12 & 13 & 14 & 15 & 16 & 17 & 18 & 19 & 20 \\ 
  \hline
1 & 100.0 & -0.2 & 0.1 & 0.0 & 0.0 & 0.0 & 0.0 & 0.0 & -0.0 & -0.0 & 0.0 & 0.0 & -0.0 & -0.0 & -0.0 & -0.3 & -0.0 & 0.0 & 0.0 & 0.0 \\ 
  2 & 0.1 & 100.0 & 0.2 & 0.0 & 0.0 & 0.0 & 0.0 & 0.0 & 0.0 & -0.1 & 0.0 & -0.0 & 0.0 & -0.0 & -0.0 & 0.0 & -0.0 & -0.0 & 0.0 & 0.0 \\ 
  3 & -0.0 & -0.1 & 100.0 & -0.0 & 0.0 & -0.0 & -0.0 & -0.0 & -0.0 & 0.1 & -0.0 & 0.0 & 0.0 & -0.0 & -0.0 & -0.3 & 0.0 & 0.0 & -0.0 & -0.0 \\ 
  4 & -0.0 & -0.0 & 0.0 & 100.0 & -0.0 & 0.0 & 0.0 & 0.0 & -0.0 & -0.0 & 0.0 & 0.0 & -0.0 & -0.0 & -0.0 & 0.1 & 0.0 & 0.0 & 0.0 & 0.0 \\ 
  5 & 0.0 & -0.0 & -0.0 & 0.0 & 100.0 & 0.0 & -0.0 & 0.0 & 0.0 & -0.0 & -0.0 & 0.0 & 0.0 & 0.0 & -0.0 & 0.1 & -0.0 & -0.0 & -0.0 & 0.0 \\ 
  6 & -0.0 & -0.0 & 0.0 & -0.0 & -0.0 & 100.0 & -0.3 & 0.4 & -0.0 & 0.0 & -0.0 & 0.0 & -0.0 & -0.0 & 0.0 & -0.1 & 0.0 & -0.0 & -0.0 & 0.0 \\ 
  7 & -0.0 & -0.0 & 0.0 & -0.0 & 0.0 & 0.3 & 100.0 & -0.2 & -0.0 & 0.2 & -0.1 & -0.1 & 0.0 & 0.0 & 0.0 & 0.3 & -0.0 & -0.0 & 0.0 & -0.0 \\ 
  8 & -0.0 & -0.0 & 0.0 & -0.0 & -0.0 & -0.4 & 0.2 & 100.0 & 0.0 & 0.2 & -0.1 & -0.0 & 0.0 & 0.0 & 0.0 & 0.2 & 0.0 & 0.0 & -0.0 & 0.0 \\ 
  9 & 0.0 & -0.0 & 0.0 & 0.0 & -0.0 & 0.0 & 0.0 & -0.0 & 100.0 & 0.2 & -0.0 & 0.0 & -0.0 & -0.0 & 0.0 & -0.5 & -0.0 & 0.0 & -0.0 & 0.0 \\ 
  10 & 0.0 & 0.0 & -0.0 & 0.0 & 0.0 & -0.0 & -0.1 & -0.1 & -0.2 & 100.0 & 0.4 & -0.1 & 0.1 & 0.0 & 0.0 & 0.8 & -0.0 & -0.0 & 0.0 & 0.0 \\ 
  11 & -0.0 & -0.0 & 0.0 & -0.0 & 0.0 & 0.0 & 0.0 & 0.0 & 0.0 & -0.3 & 100.0 & 0.2 & -0.1 & -0.0 & -0.0 & -0.2 & 0.0 & 0.0 & -0.0 & 0.0 \\ 
  12 & -0.0 & 0.0 & -0.0 & -0.0 & -0.0 & -0.0 & 0.0 & 0.0 & -0.0 & 0.1 & -0.1 & 100.0 & -0.3 & 0.1 & 0.0 & 1.7 & -0.0 & -0.1 & -0.0 & -0.0 \\ 
  13 & 0.0 & -0.0 & -0.0 & 0.0 & -0.0 & 0.0 & -0.0 & -0.0 & 0.0 & -0.0 & 0.0 & 0.3 & 100.0 & -0.4 & -0.1 & -2.8 & 0.0 & 0.0 & 0.1 & 0.0 \\ 
  14 & 0.0 & 0.0 & 0.0 & 0.0 & -0.0 & 0.0 & -0.0 & -0.0 & -0.0 & -0.0 & 0.0 & -0.1 & 0.4 & 100.0 & -0.0 & -1.8 & 0.0 & 0.0 & 0.0 & -0.0 \\ 
  15 & 0.0 & 0.0 & -0.0 & 0.0 & 0.0 & -0.0 & 0.0 & -0.0 & -0.0 & -0.0 & 0.0 & -0.0 & 0.0 & -0.0 & 100.0 & -2.1 & 0.1 & -0.0 & 0.0 & 0.0 \\ 
  16 & 0.0 & 0.0 & -0.0 & -0.0 & 0.0 & -0.0 & 0.0 & -0.0 & 0.0 & 0.0 & -0.0 & 0.0 & 0.0 & 0.0 & -0.0 & 1.3 & 100.0 & 0.6 & -0.1 & -0.3 \\ 
  17 & -0.0 & -0.0 & -0.0 & 0.0 & -0.0 & -0.0 & -0.0 & 0.0 & -0.0 & -0.0 & 0.0 & 0.0 & -0.0 & -0.0 & -0.1 & -5.0 & 0.7 & -99.9 & -0.8 & -0.2 \\ 
  18 & 0.0 & 0.0 & -0.0 & 0.0 & -0.0 & -0.0 & 0.0 & 0.0 & -0.0 & 0.0 & -0.0 & 0.0 & -0.0 & -0.0 & -0.0 & -2.9 & 0.0 & 0.9 & -99.5 & 8.7 \\ 
  19 & 0.0 & 0.0 & -0.0 & 0.0 & 0.0 & 0.0 & -0.0 & 0.0 & 0.0 & 0.0 & 0.0 & -0.0 & 0.0 & -0.0 & 0.0 & -0.3 & -0.2 & 0.3 & -8.6 & -99.6 \\ 
  20 & 0.0 & 0.0 & -0.0 & 0.0 & -0.0 & -0.0 & -0.0 & 0.0 & 0.0 & 0.0 & 0.0 & -0.0 & 0.0 & 0.0 & 0.1 & 7.3 & -0.8 & -0.3 & -4.4 & -0.3 \\ 
   \hline
\end{tabular}
\end{table}

% latex table generated in R 3.6.0 by xtable 1.8-4 package
% Wed Nov 27 16:04:03 2019
\begin{table}[ht]
\caption{Correlation between first 20 PC scores of the UK Biobank, either computed using the genotyping chip and mean imputation (top), or computed from the dosages (based on imputation from an external reference panel) of the same variants (left). PCs are globally the same.
\label{tab:pca-dosage}}
\centering
\begin{tabular}{|r|rrrrrrrrrrrrrrrrrrrr|}
  \hline
 & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 & 11 & 12 & 13 & 14 & 15 & 16 & 17 & 18 & 19 & 20 \\ 
  \hline
1 & -100.0 & -0.1 & -0.1 & 0.0 & -0.0 & 0.0 & -0.0 & -0.0 & -0.0 & 0.0 & -0.0 & -0.0 & -0.0 & -0.0 & -0.0 & -0.0 & 0.0 & 0.0 & 0.0 & -0.0 \\ 
  2 & 0.1 & -100.0 & -0.2 & -0.0 & -0.0 & -0.0 & 0.0 & -0.0 & 0.0 & -0.0 & 0.0 & 0.0 & 0.0 & -0.0 & 0.0 & 0.0 & -0.0 & -0.0 & -0.0 & 0.0 \\ 
  3 & -0.1 & -0.2 & 100.0 & -0.2 & 0.0 & 0.0 & 0.1 & 0.0 & 0.0 & 0.0 & -0.0 & 0.0 & 0.0 & -0.0 & -0.0 & 0.0 & 0.0 & -0.0 & 0.0 & -0.0 \\ 
  4 & 0.0 & -0.0 & 0.2 & 100.0 & 0.1 & 0.0 & -0.1 & -0.0 & 0.0 & 0.1 & -0.0 & 0.0 & 0.0 & 0.0 & 0.0 & 0.0 & -0.0 & 0.0 & -0.0 & 0.0 \\ 
  5 & 0.0 & 0.0 & 0.0 & 0.1 & -100.0 & 0.0 & -0.0 & -0.0 & 0.0 & 0.0 & -0.0 & -0.0 & 0.0 & 0.0 & 0.0 & -0.0 & 0.0 & 0.0 & -0.0 & -0.0 \\ 
  6 & -0.0 & -0.0 & -0.0 & -0.0 & 0.0 & 99.9 & -2.7 & 2.0 & -0.0 & -0.0 & -0.0 & 0.0 & -0.0 & 0.0 & 0.0 & -0.0 & 0.0 & 0.0 & -0.0 & -0.0 \\ 
  7 & -0.0 & -0.0 & -0.1 & 0.1 & -0.0 & 2.6 & 99.9 & 3.3 & -0.1 & -0.1 & 0.0 & -0.0 & 0.0 & 0.0 & -0.0 & -0.0 & 0.0 & -0.0 & 0.0 & -0.0 \\ 
  8 & 0.0 & 0.0 & -0.0 & 0.0 & -0.0 & -2.1 & -3.2 & 99.9 & 0.2 & -0.2 & 0.0 & -0.0 & -0.0 & -0.0 & -0.0 & -0.0 & -0.0 & -0.0 & 0.0 & -0.0 \\ 
  9 & -0.0 & -0.0 & -0.0 & -0.0 & -0.0 & 0.0 & 0.1 & -0.2 & 100.0 & -0.0 & -0.0 & -0.0 & -0.0 & -0.0 & 0.0 & -0.0 & 0.0 & 0.0 & 0.0 & 0.0 \\ 
  10 & -0.0 & 0.0 & 0.1 & 0.0 & -0.0 & -0.0 & -0.1 & -0.1 & -0.0 & -99.9 & -0.3 & -0.1 & 0.0 & -0.0 & 0.0 & -0.0 & -0.0 & -0.0 & -0.0 & -0.0 \\ 
  11 & 0.0 & -0.0 & -0.0 & -0.0 & 0.0 & -0.0 & 0.0 & 0.0 & -0.0 & 0.4 & -99.9 & 0.2 & 0.1 & 0.0 & 0.0 & -0.0 & -0.0 & -0.0 & 0.0 & -0.0 \\ 
  12 & 0.0 & -0.0 & -0.0 & 0.0 & -0.0 & 0.0 & -0.0 & -0.0 & -0.0 & 0.1 & -0.2 & -99.9 & 0.7 & -0.0 & 0.1 & 0.0 & 0.0 & 0.0 & 0.0 & 0.0 \\ 
  13 & -0.0 & 0.0 & -0.0 & -0.0 & -0.0 & 0.0 & -0.0 & 0.0 & 0.0 & 0.0 & 0.1 & 0.7 & 99.9 & 2.1 & 0.0 & -0.0 & 0.0 & -0.1 & -0.0 & 0.0 \\ 
  14 & -0.0 & -0.0 & 0.0 & 0.0 & 0.0 & -0.0 & -0.0 & 0.0 & 0.0 & -0.0 & 0.0 & -0.0 & -2.1 & 99.9 & -0.1 & -0.0 & 0.0 & -0.0 & 0.0 & 0.0 \\ 
  15 & -0.0 & -0.0 & -0.0 & 0.0 & 0.0 & -0.0 & -0.0 & 0.0 & -0.0 & 0.0 & 0.0 & 0.1 & -0.0 & 0.1 & 99.9 & 0.1 & 0.0 & -0.1 & 0.1 & 0.1 \\ 
  16 & -0.0 & 0.0 & -0.0 & 0.0 & 0.0 & -0.0 & -0.0 & -0.0 & -0.0 & -0.0 & -0.0 & -0.0 & -0.0 & -0.0 & 0.0 & -99.7 & 6.4 & 0.8 & 0.9 & -1.3 \\ 
  17 & -0.0 & 0.0 & -0.0 & 0.0 & 0.0 & -0.0 & 0.0 & 0.0 & 0.0 & 0.0 & -0.0 & 0.0 & -0.0 & -0.0 & -0.0 & 6.4 & 99.6 & -1.0 & 2.4 & 0.5 \\ 
  18 & 0.0 & -0.0 & -0.0 & 0.0 & -0.0 & -0.0 & 0.0 & -0.0 & 0.0 & 0.0 & 0.0 & -0.0 & -0.1 & -0.0 & -0.1 & -0.9 & -0.9 & -99.6 & -5.0 & 4.0 \\ 
  19 & 0.0 & -0.0 & -0.0 & 0.0 & 0.0 & -0.0 & 0.0 & 0.0 & 0.0 & 0.0 & 0.0 & -0.0 & -0.0 & 0.0 & 0.1 & -0.6 & 2.5 & 4.9 & -99.5 & -6.2 \\ 
  20 & -0.0 & 0.0 & 0.0 & 0.0 & -0.0 & -0.0 & 0.0 & 0.0 & -0.0 & -0.0 & -0.0 & 0.0 & -0.0 & -0.0 & -0.0 & -1.4 & -0.2 & 4.3 & -6.0 & 99.5 \\ 
   \hline
\end{tabular}
\end{table}
